Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-18 numerical-chemistry.tex
updated chemistry to reflect matt's feedback re: D2 and HD.
small updates to correct numbering.

\end{tabular}
\caption[]{Collisional processes solved in the Enzo nonequilibrium
primordial chemistry routines. \red{Missing 3-body rate for D$_2$?}}
\label{table.collisional}
\end{center}
\end{table}

\begin{table}
\begin{center}
{\bfseries Radiative Processes}\\[1ex]
\begin{tabular}{llllllll}
(21) & H & + & $\gamma$ & $\rightarrow$ & H$^+$ & + & e$^-$ \\
(22) & He & + & $\gamma$ & $\rightarrow$ & He$^+$ & + & e$^-$ \\
(23) & He$^+$ & + & $\gamma$ & $\rightarrow$ & He$^{++}$ & + & e$^-$ \\
(24) & H$^-$ & + & $\gamma$ & $\rightarrow$ & H & + & e$^-$ \\
(25) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(26) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & H & + & H$^+$ \\
(27) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & 2H$^+$ & + & e$^-$ \\
(28) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^*$ & $\rightarrow$ & 2H \\
(29) & H$_2$ & + & $\gamma$ & $\rightarrow$ & 2H &  & 
\end{tabular}
\caption[]{Radiative processes solved in the Enzo nonequilibrium
primordial chemistry routines. \red{Missing rates for D$_2$?}}
\label{table.radiative}
\end{center}
\end{table}

>>>>

\end{tabular}
\caption[]{Collisional processes solved in the Enzo nonequilibrium
primordial chemistry routines.}
\label{table.collisional}
\end{center}
\end{table}

\begin{table}
\begin{center}
{\bfseries Radiative Processes}\\[1ex]
\begin{tabular}{llllllll}
(32) & H & + & $\gamma$ & $\rightarrow$ & H$^+$ & + & e$^-$ \\
(33) & He & + & $\gamma$ & $\rightarrow$ & He$^+$ & + & e$^-$ \\
(34) & He$^+$ & + & $\gamma$ & $\rightarrow$ & He$^{++}$ & + & e$^-$ \\
(35) & H$^-$ & + & $\gamma$ & $\rightarrow$ & H & + & e$^-$ \\
(36) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(37) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & H & + & H$^+$ \\
(38) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & 2H$^+$ & + & e$^-$ \\
(39) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^*$ & $\rightarrow$ & 2H \\
(40) & H$_2$ & + & $\gamma$ & $\rightarrow$ & 2H &  & 
\end{tabular}
\caption[]{Radiative processes solved in the Enzo nonequilibrium
primordial chemistry routines. \red{Missing rates for HD destruction/ionization?}}
\label{table.radiative}
\end{center}
\end{table}
